Statically Typed String Sanitation Inside a Python (Technical Report)

### 2014-12-16 sanitation-psp14/tr/strings_chapter.tex
lambdap preservation.

\todo{Everything above in this proof was sleep deprived plane work -- need to check}

@@

@@

\inferrule[P-T-Check]
{\tctx \vdash \iota_r : \regex \\ \tctx \vdash \iota_1 : \str \\ \tctx \vdash \iota_2 : \sigma \\ \tctx \vdash \iota_3 : \sigma}
{\tctx \vdash \tcheck{\iota_r}{\iota_1}{\iota_2}{\iota_3} : \sigma}
\end{mathpar}
\caption{Typing rules for $\lambdap$.
The typing context $\tctx$ is standard.}
\label{fig:slambdap}
\end{figure}

@@

\inferrule[PS-E-Check-Left]
{ \iota_x \mapsto \iota_x' }
{ \check{\iota_x}{\iota}{\iota_1}{\iota_2} \mapsto \check{\iota_x}{\iota}{\iota_1}{\iota_2} }

\inferrule[PS-E-Check-Right]
{ \iota \mapsto \iota' }
{ \check{\rx{r}}{\iota}{\iota_1}{\iota_2} \mapsto \check{\rx{r}}{\iota'}{\iota_1}{\iota_2} }

\inferrule[PS-E-Check-OK]
{ s \in \lang{r} }
{ \check{\rx{r}}{\tstr{s}}{\iota_1}{\iota_2} \mapsto \iota_1}

\inferrule[PS-E-Check-NotOK]
{ s \not\in \lang{r} }
{ \check{\rx{r}}{\tstr{s}}{\iota_1}{\iota_2} \mapsto \iota_2}

>>>>

\todo{Everything above in the $\lambdap$ section was sleep deprived plane work -- need to check}

@@

\item \textbf{Case PS-E-CheckLeft}
Let $\iota = \rcheck{\iota_x}{\iota_1}{\iota_2}{\iota_3} \mapsto \rcheck{\iota_x'}{\iota_1}{\iota_2}{\iota_3}$
where $\iota_x \mapsto \iota_x'$.
The applicable typing rule is P-T-Check, so $\emptyset \vdash \iota : \tau$ where:
\begin{align*}
  \emptyset &\vdash \iota_x : \regex \\
  \emptyset &\vdash \iota_1 : \str \\
  \emptyset &\vdash \iota_2 : \tau \\
  \emptyset &\vdash \iota_3 : \tau
\end{align*}
By induction, $\iota_x : \regex$. Therefore,
$\emptyset \rcheck{\iota_x'}{\iota_1}{\iota_2}{\iota_3} : \tau$.

\item \textbf{Case PS-E-CheckRight}
Let $\iota = \rcheck{\iota_x}{\iota_1}{\iota_2}{\iota_3} \mapsto \rcheck{\iota_x}{\iota_1'}{\iota_2}{\iota_3}$
where $\iota_1 \mapsto \iota_1'$.
The applicable typing rule is P-T-Check, so $\emptyset \vdash \iota : \tau$ where:
\begin{align*}
  \emptyset &\vdash \iota_x : \regex \\
  \emptyset &\vdash \iota_1 : \str \\
  \emptyset &\vdash \iota_2 : \tau \\
  \emptyset &\vdash \iota_3 : \tau
\end{align*}
By induction, $\iota_1' : \str$. Therefore,
$\emptyset \rcheck{\iota_x}{\iota_1'}{\iota_2}{\iota_3} : \tau$.

\item \textbf{Case PS-E-Check-Ok} 
Let $\iota = \rcheck{\rx{r}}{\rstr{s}}{\iota_2}{\iota_3} \mapsto \iota_2$ and $s \in \lang{r}$.
The applicable typing rule is P-T-Check, so $\emptyset \vdash \iota : \tau$ where
$\emptyset \vdash \iota_2 : \tau$.

\item \textbf{Case PS-E-Check-NotOk} 
Let $\iota = \rcheck{\rx{r}}{\rstr{s}}{\iota_2}{\iota_3} \mapsto \iota_3$ where $s \not \in \lang{r}$.
The applicable typing rule is P-T-Check, so $\emptyset \vdash \iota : \tau$ where
$\emptyset \vdash \iota_3 : \tau$.

@@

\inferrule[P-T-Check]
{\tctx \vdash \iota_x : \regex \\ \tctx \vdash \iota_1 : \str \\ \tctx \vdash \iota_2 : \tau \\ \tctx \vdash \iota_3 : \tau}
{\tctx \vdash \tcheck{\iota_x}{\iota_1}{\iota_2}{\iota_3} : \tau}
\end{mathpar}
\caption{Typing rules for $\lambdap$.
The typing context $\tctx$ is standard.}
\label{fig:slambdap}
\end{figure}

@@

\inferrule[PS-E-CheckLeft]
{ \iota_x \mapsto \iota_x' }
{ \rcheck{\iota_x}{\iota}{\iota_1}{\iota_2} \mapsto \rcheck{\iota_x}{\iota}{\iota_1}{\iota_2} }

\inferrule[PS-E-CheckRight]
{ \iota \mapsto \iota' }
{ \rcheck{\rx{r}}{\iota}{\iota_1}{\iota_2} \mapsto \rcheck{\rx{r}}{\iota'}{\iota_1}{\iota_2} }

\inferrule[PS-E-Check-OK]
{ s \in \lang{r} }
{ \rcheck{\rx{r}}{\tstr{s}}{\iota_1}{\iota_2} \mapsto \iota_1}

\inferrule[PS-E-Check-NotOK]
{ s \not\in \lang{r} }
{ \rcheck{\rx{r}}{\tstr{s}}{\iota_1}{\iota_2} \mapsto \iota_2}
